Asymptotic-Preserving Discretization of Three-Dimensional Plasma Fluid Models

### 2024-03-07 paper_version/rebuttal_letter.tex

%-----------------------------------------------------------------------------%
\documentclass[a4paper, 10pt]{letter}

\usepackage[utf8]{inputenc}
\usepackage{enumitem}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{bm}
\usepackage{hyperref}
\usepackage{geometry}
\usepackage{xcolor}
\geometry{a4paper,scale=0.8}

%-----------------------------------------------------------------------------%

\begin{document}

\begin{letter}
\opening{Dear Editors,}

We thank the reviews for the generous and insightful comments on our work and have revised the manuscript to address their concerns. The corresponding replies for each comments are attached in the end.

We believe that the manuscript is now suitable for publication.

\closing{On behalf of all authors,\\ \vspace{1cm} Tianwei Yu}
\end{letter}

\newpage

\begin{itemize}
  \item Question 1.1: \textcolor{violet}{Can the new 3D scheme reduces to Degond's 1D scheme?}
  \item[$\blacktriangleright$] Reply: \textcolor{blue}{
  Yes. The proposed numerical scheme in 3D is a natural extension of the 1D
  the scheme proposed by Degond et. al. This is justified by considering problems with
  transverse invariance (namely, variables keep constant along the x-axis and y-axis) and
  verifying that the "projected" 3D scheme coincides with the original 1D scheme at the z-axis.
  Section~4.1 is devoted to such a purpose. To better clarify this point, we add a remark
  right after the 3D full discretization: ``When applying the ``projection to one dimension"
  described in Section~4.1.1, the fully discrete 3D AP scheme (32) collapses to (31)
  discretization proposed in $[$P.~Degond, F.~Deluzet, and D.~Savelief, \emph{Numerical approximation of the Euler-Maxwell model in the quasineutral limit}, Journal of Computational Physics, 231 (4), pp.~1917--1946, 2012$]$. This is not a coincidence, because
  recovering of (31) under dimensional reduction has guided our construction."
  }

  \item Question 1.2: \textcolor{violet}{In Fig 8, Page 19, it seems the 1D results are better than the 3D results by using the same meshes. Can the new 3D scheme
  preserve some good properties of the original 1D scheme?}
  \item[$\blacktriangleright$] Reply: \textcolor{blue}{
  Technically speaking, Fig.~8 is a ``verification" rather than a ``comparison".
  The result produced by the 3D scheme, as illustrated in Section~5.1, is the
  solution along the z-axis for the cylindrical setting in Fig.~2. To better
  clarify this point, we add some comments in the description of Fig.~8:
  ``... The 3D result is generated under the setting in Fig.~2
  and restricted to the z-axis. The results are slightly different from
  the 1D result probably due to the impact of the outer boundary of the
  cylindrical domain."
  }

  \item Question 1.3: \textcolor{violet}{In numerical tests, the mass ratio and the collision parameter are computed by a constant number. Is it sufficient to
demonstrate the good performance of the new scheme?}
  \item[$\blacktriangleright$] Reply: \textcolor{blue}{
  We agree that the robustness with respect to the mass ratio and the collision parameter
  is worth studying in dealing with the plasma model.
  However, the objective of the proposed scheme is stability with respect to
  the Debye length $\lambda$. The impacts of the mass ratio and the collision parameter
  are not of our central interest.
  In fact, our scheme does not possess uniform stability over the mass ratio $\varepsilon_*$
  yet has it over the collision parameter $\alpha^{\text{coll}}$. This can be
  inferred from (32j) by noticing the explicit term
  $\varepsilon_*^{-2}q_*(n\mathbf{u})_*^m \times \mathbf{B}^m$
  and the implicit terms
  $\varepsilon_*^{-2}\mathbf{R}^{\text{coll}, m+1}_*, \varepsilon_*^{-2}Q^{\text{coll}, m+1}_*$.
  It seems possible to achieve stability over the mass ratio $\varepsilon_*$
  by replacing $\varepsilon_*^{-2}q_*(n\mathbf{u})_*^m \times \mathbf{B}^m$
  by $\varepsilon_*^{-2}q_*(n\mathbf{u})_*^{m+1} \times \mathbf{B}^{m}$.
  However, this would significantly change the time-stepping procedure.
  We decide not to pursue this and want to be aligned with Degond's scheme.
  }

  \item Question 1.4: \textcolor{violet}{Include the following references:
  [Fast-Converging and Asymptotic-Preserving Simulation of Frequency Domain Thermoreflectance, Jia Liu \& Lei Wu. Commun. Comput. Phys., 34 (2023), pp. 65-93.]
  [A Coupled FEM-BEM Approach for the Solution of the Free-Boundary Axi-Symmetric Plasma Equilibrium Problem. M. Bonotto, D. Abate, P. Bettni \& F. Villone. Commun. Comput. Phys., 31 (2022), pp. 27-59.]}
  \item[$\blacktriangleright$] Reply: \textcolor{blue}{Both paper is included in the introduction.
  The first paper is added to the literature review on AP schemes
  while the second one is mentioned when the symmetry of the problem is discussed.}
\end{itemize}

\newpage

\begin{itemize}
  \item Question 2.1: \textcolor{violet}{The literature review provided in the paper is incomplete.
  Numerous structure-preserving schemes for plasma models involving the Euler
  and Maxwell equations exist, such as the compressible ideal MHD model.
  Relevant works should include, but not be limited to:
  \begin{itemize}
      \item[1)] The positivity-preserving and divergence-free finite volume schemes and
  central discontinuous Galerkin schemes (also using the primal and dual meshes);
  see, e.g., [K. Wu, SIAM Journal on Numerical Analysis, 56(4):2124-2147, 2018]
  and [K. Wu, H. Jiang, and C.-W. Shu, SIAM Journal on Numerical Analysis, 61: 250-285, 2023].
      \item[2)] These schemes are designed by using the geometric quasilinearization framework in
  [K. Wu and C.-W. Shu, SIAM Review, 65(4):1031-1073, 2023],
  where the multicomponent MHD equations for multi-species plasma were also studied.
      \item[3)] High-order asymptotic preserving (AP) finite difference WENO schemes with
  constrained transport were also developed for MHD equations in
  [W. Chen, K. Wu, and T. Xiong, Journal of Computational Physics, 488: 112240, 2023].
  \end{itemize}}

  \item[$\blacktriangleright$] Reply: \textcolor{blue}{
  We have added a paragraph at the end of Section~2.2. A short discussion and literature
  review on the numerical methods for plasma models is presented with a focus on the
  structure-preserving property. The literature mentioned in 3) is included in the
  literature review in Section~1 when discussing AP schemes.
  }

  \item Questions 2.2: \textcolor{violet}{The author did not provide an accuracy test
  for the convergence rate of their proposed numerical method.
  An illustrative example can be found in section 6.2 of
  [K. Wu, H. Jiang, and C.-W. Shu, SIAM Journal on Numerical Analysis, 61: 250-285, 2023],
  as well as in Examples 5.1 and 5.2 in [W. Chen, K. Wu, and T. Xiong, Journal of Computational Physics, 488: 112240, 2023]}
  \item[$\blacktriangleright$] Reply: \textcolor{blue}{
  To handle this issue, we put some effort into re-devising the matrix assembly which
  now admits a fast iterative solver such that reference solutions on sufficiently refined
  meshes are possible. A new case involving a cuboid domain is tested and
  $L^1$ and $L^2$ errors at different values of $\lambda$ are reported in the same manner as suggested by the second paper.
  A smooth test case seems hard to construct due to the presence of the interface of two different
  electromagnetic boundary conditions in our underlying setting depicted in Fig.~2.
  }

  \item Question 2.3: \textcolor{violet}{
  Limited Numerical Examples: All the numerical examples provided in the paper
  are either one-dimensional or three-dimensional cylindrical. To strengthen the paper's contribution,
  it is advisable to include a genuinely three-dimensional example.
  This is especially relevant as one of the primary contributions of the paper lies in the
  extension of a one-dimensional scheme to three dimensions.
  }
  \item[$\blacktriangleright$] Reply: \textcolor{blue}{
  We include a slightly more general 3D case in Case IV. Yet we would like to mention that 
  our current framework of primal-dual mesh generation is based on the idea of
  ``extruding 2D mesh" in Sec.~4.2.1 of
  $[$Marrone, Massimiliano.\emph{Computational Aspects of the Cell Method in Electrodynamics - Abstract.} Journal of Electromagnetic Waves and Applications 15 (2001): 407 - 408.$]$.
  It has not been extended yet to arbitrary geometries, which possibly takes quite some effort.
  Therefore, we have decided to defer this part to future work. Nevertheless,
  the proposed scheme can be directly applied to arbitrary domains
  as long as the primal-dual meshes are generated properly.
  }
\end{itemize}

\end{document}
%-----------------------------------------------------------------------------%

### 2024-03-07 paper_version/main.tex
review

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{enumitem}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{bm}
\usepackage{hyperref}
\usepackage{geometry}
\geometry{a4paper,scale=0.8}
\usepackage[square,numbers]{natbib}
\bibliographystyle{abbrvnat}
\usepackage{tikz}
\usepackage{tkz-euclide}
\usetikzlibrary{positioning, decorations.markings, arrows, intersections}
\usepackage{nicematrix}
\NiceMatrixOptions{cell-space-top-limit = 4pt}
\NiceMatrixOptions{cell-space-bottom-limit = 4pt}
\usepackage{tcolorbox}
\usepackage{caption, subcaption}
\captionsetup[figure]{labelfont={bf},name={Fig.},labelsep=period}
\captionsetup[table]{labelfont={bf},name={Tab.},labelsep=period}
\setlength\arrayrulewidth{0.7pt}
\usepackage{authblk}
\usepackage{soul}
%\usepackage{showlabels}
\usepackage{multirow}

@@

@@

We stay close to \cite{degond_2012} in terms of discretization in time employing
semi-implicit time-stepping. We also base our considerations on the model geometry shown
in Fig.~\ref{fig:domain_geometry}. We would like to remark that the mesh-based numerical
scheme proposed in this paper can in principle be adapted to geometric situations much
more general than that of Fig.~\ref{fig:domain_geometry}. However, one may encounter
subtle problems in defining proper dual meshes as we need it in Section
\ref{sec:mesh-duality}. Thus, for the sake of simplicity of presentation we forgo
geometric generality.

The quasi-neutral limit of the Maxwell-Euler system leads to a singularly perturbed
problem, that is, the limiting PDE system changes its type\footnote{The type of the
  Maxwell-Euler system switches from hyperbolic to mixed for $\lambda_{D}\to 0$}. This
poses a challenge for simulations in settings encompassing different regimes. We remind
that singularly perturbed problems occur in many physical models, e.g., in the case of
vanishing viscosity in the Navier-Stokes equations \cite{Kato_1984}, the
zero-relaxation-limit of kinetic equations \cite{jin_2010}, and the zero-Mach-number limit
of compressible flows \cite{degond_2007, haack_2010}. Throughout, it is essential that
numerical schemes remain valid even if crucial model parameters approach the limit. These
schemes are then said to be \emph{asymptotic-preserving} (AP): Let us assume that we
discretize a parameter($\lambda$)-dependent model $P^\lambda$, which converges to a limit
$P^0$ as $\lambda \rightarrow 0$, by the scheme $P^\lambda_h$ where $h$ denotes some
discretization parameter, e.g., the mesh size. The AP property amounts to uniform
convergence of $P^\lambda_h$ to the $P^\lambda$ as $\lambda\rightarrow0$. Readers are
referred to the illustration by a commuting diagram in \cite[][Fig.~1]{jin_2010} and, more
generally, to the comprehensive reviews \cite{jin_2010, degond_2017} for more details
about AP schemes.

@@

\begin{figure}
    \centering
    \begin{tikzpicture}[scale=1.2]
    \coordinate (O1) at (0,0);
    \draw[violet] (O1) circle (1) node[blue] {Electrode};
    \fill[blue, opacity=0.2] (O1) circle (1);
    \draw[very thick] (O1) circle (1.5);
    \coordinate (O2) at (4.5,1);
    \draw[violet] (O2) circle (1);
    \node at (O2) {\textcolor{red}{Electrode}};
    \node at (barycentric cs:O1=1,O2=1) {Plasma}; 
    \fill[red, opacity=0.2] (O2) circle (1);
    \coordinate (S1) at ([shift={(-0.196,0.98)}]O1);
    \coordinate (S2) at ([shift={(-0.196,0.98)}]O2);
    \coordinate (P1) at ([shift={(0.196,-0.98)}]O1);
    \coordinate (P2) at ([shift={(0.196,-0.98)}]O2);
    \draw[violet] (S1) -- (S2);
    \draw[violet] (P1) -- (P2);
    \coordinate (SS1) at ([shift={({-0.196*1.5},{0.98*1.5})}]O1);
    \coordinate (SS2) at ([shift={({-0.196*1.5},{0.98*1.5})}]O2);
    \coordinate (PP1) at ([shift={({0.196*1.5},{-0.98*1.5})}]O1);
    \coordinate (PP2) at ([shift={({0.196*1.5},{-0.98*1.5})}]O2);
    \draw[very thick] (SS1) -- (SS2);
    \draw[very thick] (PP1) -- (PP2); 
    \draw[black, very thick] (SS2) arc (101.31:180+101.31:1.5);
    \draw[very thick] (PP2) arc (101.31-180:101.31:1.5);
    \draw[-to] (barycentric cs:SS1=1,SS2=1,S1=1,S2=1) to[out=90,in=0] ([shift={(-0.5,0.5)}]barycentric cs:SS1=1,SS2=1,S1=1,S2=1) node[left, gray] {Insulator};
    \begin{scope}[shift={(5.5,-1.4)}]
    \draw[blue, -to] (0,0) -- (0.65,0.12) node[right]{\small $z$};
    \draw[blue, -to] (0,0) -- (0,0.7) node[above]{\small $x$};
    \draw[blue, -to] (0,0) -- (0.7,0) node[below]{\small $y$};
    \end{scope}
    \end{tikzpicture}
    \caption{The special geometric setting suggested by the simulation of electric arcs,
      for which we discuss the new method.}
\label{fig:domain_geometry}
\end{figure}

@@

\begin{remark}
  \label{rem:coll}
  For the sake of simplicity, we only consider ion-electron collision in this work, but
extension to more species is straightforward. Such collisions can be well modelled by
friction terms, for instance \citep[][Sec. 5.6.2]{chen2016}
\begin{equation} \label{equ:collision}
    \mathbf{R}_{e}^{\text{coll}} = \frac{\pi Ze^4m_e^{1/2}}{(4\pi\epsilon)^2(k_BT_e)^{3/2}}\text{\emph{ln}}\Lambda n_en_i(\mathbf{u}_i - \mathbf{u}_e) = - \mathbf{R}_{i}^{\text{coll}},  
\end{equation}
which is the collision force acting on electrons. \emph{ln}$\Lambda$ is called the \emph{Coulomb
  logarithm} and is usually taken as a constant \cite{chen2016}. Because of the
conservation of momentum, the collision term for ions $\mathbf{R}_{i}^{\text{coll}}$ is
nothing but the negative of $\mathbf{R}_{e}^{\text{coll}}$. In this work, the other
effects, e.g. ionization and recombination, are not considered. For full details about the
modeling of these physical processes, readers are referred to
\cite[][Sec. 3.2]{fuchs_2021}.
\end{remark}

\subsection{Rescaling}
\label{sec:rescaling}
% In rescaling, variables in equations are replaced by the ratio of original quantities and constant reference quantities, which transforms the system into dimensionless form. In this part, the rescaling procedure mostly follows that of \cite[][Sec. 2.2]{degond_2017}.

We arrive at non-dimensional equations by following the rescaling procedure of
\cite[][Sec. 2.2]{degond_2017}.  First, a reference value for each quantity is
fixed. We define $\overline{x}$ and $\overline{t}$ as space and time scale of
interest, by which the reference velocity $\overline{v}$ is defined as
$\overline{x}/\overline{t}$. The typical magnitudes of electromagnetic fields are
$\overline{E}$ and $\overline{B}$. The reference magnitudes of fluid quantities are
denoted by $\overline{u}$ for the plasma drift velocity, $\overline{n}$ for the plasma number
density, $\overline{T}$ for the plasma temperature. On top of that, the reference pressure is
set to $\overline{n}k_B\overline{T}$ with $k_B$ being the Boltzmann constant; the
reference value for the specific total energy and enthalpy is set to
$\overline{u}^2$. Also taking into account the physical constants, i.e. the reference
permittivity $\overline{\epsilon}$, the reference permeability $\overline{\mu}$, the light
speed $c^2 = (\overline{\epsilon}\overline{\mu})^{-1}$, Boltzmann constant $k_B$, the
elementary charge $e$, and ion mass $m_i$, we introduce the following dimensionless
parameters:
\begin{align*} 
  \xi &:= \frac{\overline{v}}{c} \text{ the velocity of interest \emph{w.r.t.}\footnotemark[1] the light speed}, &\\
  \zeta &:= \frac{\overline{u}}{\overline{v}} \text{ the plasma velocity \emph{w.r.t.} the speed of interest}, &\\
  M &:= \frac{\overline{u}}{v_i^{\text{th}}} \text{ the plasma drift velocity \emph{w.r.t.} the thermal speed of ions, where } v_i^{\text{th}} := \left(\frac{k_B \overline{T}}{m_i}\right)^{1/2}, &\\
  \eta &:= \frac{e\overline{E}\overline{x}}{m_i\overline{u}^2} \text{ the electric energy \emph{w.r.t.} the kinetic energy of ions}, &\\
  \beta &:= \frac{\overline{v}\overline{B}}{\overline{E}} \text{ the induced electric field \emph{w.r.t.} the total electric field}, &\\
  \lambda &:= \frac{\lambda_D}{\overline{x}} \text{ the dimensionless Debye length, where }\lambda_D := \left(\frac{\epsilon k_B\overline{T}}{e^2\overline{n}}\right)^{1/2}, &\\
  \varepsilon_*^2 &:= \frac{m_*}{m_i} \text{ the species mass \emph{w.r.t.} the ion mass},\ \  * \in \{i,e,\cdots\}, &\\
  g &:= \frac{1}{\overline{n}\lambda_D^3} \text{ the plasma parameter\footnotemark[2]}.&
\end{align*}
\footnotetext[1]{Abbreviation of \emph{with respect to}.}
\footnotetext[2]{It is basically the reciprocal of the number of particles per Debye sphere, see \cite[][Sec. 1.1]{gibbon2020}. Classical plasma theory assumes $g \ll 1$.}

@@

Assumptions can be made to reduce the number of dimensionless parameters. Following
\cite[][Sec. 2.2]{degond_2017}, the reference speed $\overline{v}$ is of the same scale as
the plasma speed $\overline{u}$ and the thermal speed $v_i^{\text{th}}$ whereas it is much
smaller than the light speed $c$. Also, it is assumed that $\eta$ and $\beta$ are of order
one and $\xi$ has the same magnitude as $\lambda$.

@@

The Debye length $\lambda_D$ is the characteristic length over which the local net charge is
shielded, see \cite[Sec. 1.4]{chen2016} for the underlying physics. In many situations, it
has a very small value compared to the reference length scale: the typical $\lambda_D$ for
gas discharge and Tokamak fusion reactors is $10^{-4}$ meter, for interstellar medium, the
magnitude is about $1$ meter \cite[Ch. 20]{Blandford_2013}. Then the quasi-neutrality
assumption $\rho = \sum_* q_*n_* \approx 0$ is justified, which is typical of the limit
model.  Formally we obtain it by setting the rescaled Debye length $\lambda$ to zero in
\eqref{resc}:
\begin{center}
    \begin{minipage}{0.3\textwidth}
    \begin{align*}
        \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0 \tag{\ref{equ:maxwell_faraday_rescaled}},\\ 
        \lambda^2 \partial_t \mathbf{D} - \nabla \times \mathbf{H} &= - \mathbf{J}, \tag{\ref{equ:maxwell_ampere_rescaled}}\\
        \nabla \cdot \mathbf{B} &= 0, \tag{\ref{equ:maxwell_gauss_B_rescaled}}\\
        \lambda^2 \nabla \cdot \mathbf{D} &= \rho. \tag{\ref{equ:maxwell_gauss_D_rescaled}}
    \end{align*}
\end{minipage}
\hspace{0.6cm}$\xrightarrow[]{\lambda \rightarrow 0}$
\begin{minipage}{0.3\textwidth}
  \begin{subequations}
    \label{limit}
\begin{align}
    \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0, \label{equ:maxwell_faraday_limit} \\ 
    - \nabla \times \mathbf{H} &= - \mathbf{J}, \label{equ:maxwell_ampere_limit} \\
    \nabla \cdot \mathbf{B} &= 0,  \label{equ:maxwell_gauss_B_limit}\\
     0 &= \rho. \label{equ:maxwell_gauss_D_limit}
\end{align}
\end{subequations}
\end{minipage}
\end{center}
The quasi-neutrality condition (\ref{equ:maxwell_gauss_D_limit}) is the consequence of
setting $\lambda = 0$ in Gauss's law for the electric field
(\ref{equ:maxwell_gauss_D_rescaled}). As in the non-neutral case, Gauss's laws
(\ref{equ:maxwell_gauss_B_limit}) (\ref{equ:maxwell_gauss_D_limit}) are the consequence of
(\ref{equ:maxwell_faraday_limit}) (\ref{equ:maxwell_ampere_limit}) provided
(\ref{equ:maxwell_gauss_B_limit}) (\ref{equ:maxwell_gauss_D_limit}) are satisfied at
initial time.

@@

\begin{remark}
  The preceding formal limit argument is heuristic. Deep mathematical tools from
  perturbation theory would be needed to rigorously prove the convergence of the limiting
  sequence. This topic is beyond the scope of this paper. Readers are referred to
  \cite[Ch. 2]{remi_2014} \cite{Peng_2008} for the quasi-neutral limit of the
  Maxwell-Euler system and \cite{mark_1995, Eckhaus_1980} for the general theory.
\end{remark}

>>>>

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{enumitem}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{bm}
\usepackage{hyperref}
\usepackage{geometry}
\geometry{a4paper,scale=0.8}
\usepackage[square,numbers]{natbib}
\bibliographystyle{abbrvnat}
\usepackage{tikz}
\usepackage{tkz-euclide}
\usetikzlibrary{positioning, decorations.markings, arrows, intersections}
\usepackage{nicematrix}
\NiceMatrixOptions{cell-space-top-limit = 4pt}
\NiceMatrixOptions{cell-space-bottom-limit = 4pt}
\usepackage{tcolorbox}
\usepackage{caption, subcaption}
\captionsetup[figure]{labelfont={bf},name={Fig.},labelsep=period}
\captionsetup[table]{labelfont={bf},name={Tab.},labelsep=period}
\setlength\arrayrulewidth{0.7pt}
\usepackage{authblk}
\usepackage{soul}
%\usepackage{showlabels}
\usepackage{multirow}
\usepackage{comment}

@@

\def\ifUpdate{1}

\newcommand{\review}[1]{\textcolor{blue}{\if\ifUpdate1\textbf{#1}\fi}}
\newcommand{\reviewDel}[1]{\begin{comment} #1 \end{comment}}

@@

We stay close to \cite{degond_2012} in terms of discretization in time employing
semi-implicit time-stepping. We base our illustration on the model case shown
in Fig.~\ref{fig:domain_geometry}. Yet we would like to remark that the mesh-based numerical
scheme proposed in this paper can in principle be adapted to geometric situations much
more general than that of Fig.~\ref{fig:domain_geometry}. \review{In particular, we do not 
assume the solution to enjoy the rotational symmetry. If the symmetry is assumed, 
it can be exploited for reduction to two spatial dimensions \cite{bonotto_2022}.}

The quasi-neutral limit of the Maxwell-Euler system leads to a singularly perturbed
problem, that is, the limiting PDE system changes its type\footnote{The type of the
  Maxwell-Euler system switches from hyperbolic to mixed for $\lambda_{D}\to 0$}. This
poses a challenge for simulations in settings encompassing different regimes. 
Beside the quasi-neutral limit, we remind
that singularly perturbed problems occur in extensively many physical models, 
e.g., in the case of vanishing viscosity problem \cite{Kato_1984, bianchini_2005, temam_1997}, the
zero-relaxation-limit of kinetic-type equations \cite{raymond_2009, degond_1996}, and the incompressible limit
of compressible flows \cite{klainerman_1981}. Throughout, it is essential that
numerical schemes remain valid even if crucial model parameters approach the limit. These
schemes are then said to be \emph{asymptotic-preserving} (AP): Let us assume that we
discretize a parameter($\lambda$)-dependent model $P^\lambda$, which converges to a limit
$P^0$ as $\lambda \rightarrow 0$, by the scheme $P^\lambda_h$ where $h$ denotes some
discretization parameter, e.g., the mesh size. The AP property amounts to uniform
convergence of $P^\lambda_h$ to the $P^\lambda$ as $\lambda\rightarrow0$. 
The concept is effectively depicted by a commuting diagram in \cite[][Fig.~1]{jin_2010}. 
\review{AP schemes have been extensively studied for various problems, e.g. the diffusive limit of the kinetic equations \cite{jin_1999, liu_2023}, 
the low Mach-number limit of compressible flows \cite{degond_2007, haack_2010} and magnetohydrodynamics\cite{chen_2023}, 
the quasi-neutral limit of drift-diffusion equations \cite{chatard_2014, claire_2007}. 
More generally, readers are referred to the comprehensive reviews \cite{jin_2010, degond_2017}.}

@@

\begin{figure}
    \centering
    \begin{tikzpicture}[scale=1.2]
    \coordinate (O1) at (0,0);
    \draw[violet] (O1) circle (1) node[blue] {Electrode};
    \fill[blue, opacity=0.2] (O1) circle (1);
    \draw[very thick] (O1) circle (1.5);
    \coordinate (O2) at (4.5,1);
    \draw[violet] (O2) circle (1);
    \node at (O2) {\textcolor{red}{Electrode}};
    \node at (barycentric cs:O1=1,O2=1) {Plasma}; 
    \fill[red, opacity=0.2] (O2) circle (1);
    \coordinate (S1) at ([shift={(-0.196,0.98)}]O1);
    \coordinate (S2) at ([shift={(-0.196,0.98)}]O2);
    \coordinate (P1) at ([shift={(0.196,-0.98)}]O1);
    \coordinate (P2) at ([shift={(0.196,-0.98)}]O2);
    \draw[violet] (S1) -- (S2);
    \draw[violet] (P1) -- (P2);
    \coordinate (SS1) at ([shift={({-0.196*1.5},{0.98*1.5})}]O1);
    \coordinate (SS2) at ([shift={({-0.196*1.5},{0.98*1.5})}]O2);
    \coordinate (PP1) at ([shift={({0.196*1.5},{-0.98*1.5})}]O1);
    \coordinate (PP2) at ([shift={({0.196*1.5},{-0.98*1.5})}]O2);
    \draw[very thick] (SS1) -- (SS2);
    \draw[very thick] (PP1) -- (PP2); 
    \draw[violet] (SS2) arc (101.31:180+101.31:1.5);
    \draw[very thick] (PP2) arc (101.31-180:101.31:1.5);
    \draw[-to] (barycentric cs:SS1=1,SS2=1,S1=1,S2=1) to[out=90,in=0] ([shift={(-0.5,0.5)}]barycentric cs:SS1=1,SS2=1,S1=1,S2=1) node[left, gray] {Insulator};
    \begin{scope}[shift={(5.5,-1.4)}]
    \draw[blue, -to] (0,0) -- (0.65,0.12) node[right]{\small $z$};
    \draw[blue, -to] (0,0) -- (0,0.7) node[above]{\small $x$};
    \draw[blue, -to] (0,0) -- (0.7,0) node[below]{\small $y$};
    \end{scope}
    \end{tikzpicture}
    \caption{The special geometric setting suggested by the simulation of electric arcs,
      for which we discuss the new method.}
\label{fig:domain_geometry}
\end{figure}

@@

\begin{remark}
  \label{rem:coll}
  For the sake of simplicity, we only consider ion-electron collision in this work, but
extension to more species is straightforward. Such collisions can be well modelled by
friction terms, for instance \citep[][Sec.~5.6.2]{chen2016}
\begin{equation} \label{equ:collision}
    \mathbf{R}_{e}^{\text{coll}} = \frac{\pi Ze^4m_e^{1/2}}{(4\pi\epsilon)^2(k_BT_e)^{3/2}}\text{\emph{ln}}\Lambda n_en_i(\mathbf{u}_i - \mathbf{u}_e) = - \mathbf{R}_{i}^{\text{coll}},  
\end{equation}
which is the collision force acting on electrons. \emph{ln}$\Lambda$ is called the \emph{Coulomb
  logarithm} and is usually taken as a constant \cite{chen2016}. Because of the
conservation of momentum, the collision term for ions $\mathbf{R}_{i}^{\text{coll}}$ is
nothing but the negative of $\mathbf{R}_{e}^{\text{coll}}$. In this work, the other
effects, e.g. ionization and recombination, are not considered. For full details about the
modeling of these physical processes, readers are referred to
\cite[][Sec.~3.2]{fuchs_2021}.
\end{remark}

\subsection{Rescaling}
\label{sec:rescaling}
% In rescaling, variables in equations are replaced by the ratio of original quantities and constant reference quantities, which transforms the system into dimensionless form. In this part, the rescaling procedure mostly follows that of \cite[][Sec.~2.2]{degond_2017}.

We arrive at non-dimensional equations by following the rescaling procedure of
\cite[][Sec.~2.2]{degond_2017}.  First, a reference value for each quantity is
fixed. We define $\overline{x}$ and $\overline{t}$ as space and time scale of
interest, by which the reference velocity $\overline{v}$ is defined as
$\overline{x}/\overline{t}$. The typical magnitudes of electromagnetic fields are
$\overline{E}$ and $\overline{B}$. The reference magnitudes of fluid quantities are
denoted by $\overline{u}$ for the plasma drift velocity, $\overline{n}$ for the plasma number
density, $\overline{T}$ for the plasma temperature. On top of that, the reference pressure is
set to $\overline{n}k_B\overline{T}$ with $k_B$ being the Boltzmann constant; the
reference value for the specific total energy and enthalpy is set to
$\overline{u}^2$. Also taking into account the physical constants, i.e. the reference
permittivity $\overline{\epsilon}$, the reference permeability $\overline{\mu}$, the light
speed $c^2 = (\overline{\epsilon}\overline{\mu})^{-1}$, Boltzmann constant $k_B$, the
elementary charge $e$, and ion mass $m_i$, we introduce the following dimensionless
parameters:
\begin{align*} 
  \xi &:= \frac{\overline{v}}{c} \text{ the velocity of interest \emph{w.r.t.}\footnotemark[1] the light speed}, &\\
  \zeta &:= \frac{\overline{u}}{\overline{v}} \text{ the plasma velocity \emph{w.r.t.} the speed of interest}, &\\
  M &:= \frac{\overline{u}}{v_i^{\text{th}}} \text{ the plasma drift velocity \emph{w.r.t.} the thermal speed of ions, where } v_i^{\text{th}} := \left(\frac{k_B \overline{T}}{m_i}\right)^{1/2}, &\\
  \eta &:= \frac{e\overline{E}\overline{x}}{m_i\overline{u}^2} \text{ the electric energy \emph{w.r.t.} the kinetic energy of ions}, &\\
  \beta &:= \frac{\overline{v}\overline{B}}{\overline{E}} \text{ the induced electric field \emph{w.r.t.} the total electric field}, &\\
  \lambda &:= \frac{\lambda_D}{\overline{x}} \text{ the dimensionless Debye length, where }\lambda_D := \left(\frac{\epsilon k_B\overline{T}}{e^2\overline{n}}\right)^{1/2}, &\\
  \varepsilon_*^2 &:= \frac{m_*}{m_i} \text{ the species mass \emph{w.r.t.} the ion mass},\ \  * \in \{i,e,\cdots\}, &\\
  g &:= \frac{1}{\overline{n}\lambda_D^3} \text{ the plasma parameter\footnotemark[2]}.&
\end{align*}
\footnotetext[1]{Abbreviation of \emph{with respect to}.}
\footnotetext[2]{It is basically the reciprocal of the number of particles per Debye sphere, see \cite[][Sec.~1.1]{gibbon2020}. Classical plasma theory assumes $g \ll 1$.}

@@

Assumptions can be made to reduce the number of dimensionless parameters. Following
\cite[][Sec.~2.2]{degond_2017}, the reference speed $\overline{v}$ is of the same scale as
the plasma speed $\overline{u}$ and the thermal speed $v_i^{\text{th}}$ whereas it is much
smaller than the light speed $c$. Also, it is assumed that $\eta$ and $\beta$ are of order
one and $\xi$ has the same magnitude as $\lambda$.

@@

The Debye length $\lambda_D$ is the characteristic length over which the local net charge is
shielded, see \cite[Sec.~1.4]{chen2016} for the underlying physics. In many situations, it
has a very small value compared to the reference length scale: the typical $\lambda_D$ for
gas discharge and Tokamak fusion reactors is $10^{-4}$ meter, for interstellar medium, the
magnitude is about $1$ meter \cite[Chapt.~20]{Blandford_2013}. Then the quasi-neutrality
assumption $\rho = \sum_* q_*n_* \approx 0$ is justified, which is typical of the limit
model.  Formally we obtain it by setting the rescaled Debye length $\lambda$ to zero in
\eqref{resc}:
\begin{center}
    \begin{minipage}{0.3\textwidth}
    \begin{align*}
        \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0 \tag{\ref{equ:maxwell_faraday_rescaled}},\\ 
        \lambda^2 \partial_t \mathbf{D} - \nabla \times \mathbf{H} &= - \mathbf{J}, \tag{\ref{equ:maxwell_ampere_rescaled}}\\
        \nabla \cdot \mathbf{B} &= 0, \tag{\ref{equ:maxwell_gauss_B_rescaled}}\\
        \lambda^2 \nabla \cdot \mathbf{D} &= \rho. \tag{\ref{equ:maxwell_gauss_D_rescaled}}
    \end{align*}
\end{minipage}
\hspace{0.6cm}$\xrightarrow[]{\lambda \rightarrow 0}$
\begin{minipage}{0.3\textwidth}
  \begin{subequations}
    \label{limit}
\begin{align}
    \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0, \label{equ:maxwell_faraday_limit} \\ 
    - \nabla \times \mathbf{H} &= - \mathbf{J}, \label{equ:maxwell_ampere_limit} \\
    \nabla \cdot \mathbf{B} &= 0,  \label{equ:maxwell_gauss_B_limit}\\
     0 &= \rho. \label{equ:maxwell_gauss_D_limit}
\end{align}
\end{subequations}
\end{minipage}
\end{center}
The quasi-neutrality condition (\ref{equ:maxwell_gauss_D_limit}) is the consequence of
setting $\lambda = 0$ in Gauss's law for the electric field
(\ref{equ:maxwell_gauss_D_rescaled}). As in the non-neutral case, Gauss's laws
(\ref{equ:maxwell_gauss_B_limit}) (\ref{equ:maxwell_gauss_D_limit}) are the consequence of
(\ref{equ:maxwell_faraday_limit}) (\ref{equ:maxwell_ampere_limit}) provided
(\ref{equ:maxwell_gauss_B_limit}) (\ref{equ:maxwell_gauss_D_limit}) are satisfied at
initial time.

@@

\begin{remark}
  The preceding formal limit argument is heuristic. Deep mathematical tools from
  perturbation theory would be needed to rigorously prove the convergence of the limiting
  sequence. This topic is beyond the scope of this paper. Readers are referred to
  \cite[Chapt.~2]{remi_2014} \cite{Peng_2008} for the quasi-neutral limit of the
  Maxwell-Euler system and \cite{mark_1995, Eckhaus_1980} for the general theory.
\end{remark}
